Human Capital Model

### 2016-02-01 Tex/paper.tex

@@

The boundary of water consists of three parts: water-air boundary, water-person boundary, and water-bathtub boundary. We denote them as
${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$ respectively.

Since person is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
as the Dirichlet value condition. That is
\begin{equation}
 u=u_2, (x,y,z)\in {\Gamma}_2
\end{equation}.

@@

In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It would take several steps to calculate them.

Consider the temperature of air, $u_1$. Heat change of air consists of two aspects, heat conduction and evaporation.

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item
\item
\end{itemize}

>>>>

\begin{displaymath}
Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
\end{displaymath}

@@

The boundary of water consists of four parts: water-air boundary, water-person boundary, water-bathtub boundary, and the square for faucet. We denote them as
${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$, ${\Gamma}_4$ respectively.

Since person is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
as the Dirichlet value condition. That is
\begin{equation}
 u=u_i, (x,y,z)\in {\Gamma}_i, i=2.4
\end{equation}
In the equation, $u_2$ is the surface temperature of person. We assume it is constant. $u_4$ is the temperature of hot water.

@@

In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It takes several steps to calculate them.

Consider the temperature of air, $u_1$. Heat change of air consists of two ways, heat conduction and evaporation.

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item We change the shape of the bathtub from square to sphere and elliptical with the same strategy. The temperature graphic shows that sphere is the most proper shape for keeping water temperature. Square performs the worst on keeping temperature. However, temperature of square bathtub is more evenly than others.
\item We change the volume of the bathtub without changing its proportion. The result shows that with the same $v_h$, 
\end{itemize}
